Periodograms for Multiband Astronomical Time Series

### 2015-05-12 writeup/paper.tex
add Brandt matrix reference

\subsection{Matrix Formalism}
\sectlabel{matrix_formalism}
The expressions related to the stationary sinusoid model can be expressed more compactly by defining the following matrices:
\begin{eqnarray}
X_\omega = \left[
\begin{array}{cc}
\sin(\omega t_1) & \cos(\omega t_1)\\
\sin(\omega t_2) & \cos(\omega t_2)\\
\vdots & \vdots \\
\sin(\omega t_N) & \cos(\omega t_N)\\
\end{array}
\right]; \nonumber\\
y = \left[
\begin{array}{c}
y_1 \\
y_2\\
\vdots \\
y_N\\
\end{array}
\right];~~
\Sigma = \left[
\begin{array}{cccc}
\sigma_1^2 & 0 &  \cdots & 0\\
0 & \sigma_2^2 &  \cdots & 0\\
\vdots & \vdots &  \ddots & \vdots\\
0 & 0 &  \cdots & \sigma_N^2
\end{array}
\right]
\end{eqnarray}
With these definitions, the model in \eq{simplemodel} can be expressed as a simple linear product, $y(t|\omega,\theta) = X_\omega\theta$, and the model and reference $\chi^2$ can be written

>>>>

\subsection{Matrix Formalism}
\sectlabel{matrix_formalism}
\new{A standard way of compactly expressing least squares models is via matrix expressions \citep[See e.g.][]{Brandt1970}. Likewise,}
the expressions related to the stationary sinusoid model can be expressed more compactly by defining the following matrices:
\begin{eqnarray}
X_\omega = \left[
\begin{array}{cc}
\sin(\omega t_1) & \cos(\omega t_1)\\
\sin(\omega t_2) & \cos(\omega t_2)\\
\vdots & \vdots \\
\sin(\omega t_N) & \cos(\omega t_N)\\
\end{array}
\right]; \nonumber\\
y = \left[
\begin{array}{c}
y_1 \\
y_2\\
\vdots \\
y_N\\
\end{array}
\right];~~
\Sigma = \left[
\begin{array}{cccc}
\sigma_1^2 & 0 &  \cdots & 0\\
0 & \sigma_2^2 &  \cdots & 0\\
\vdots & \vdots &  \ddots & \vdots\\
0 & 0 &  \cdots & \sigma_N^2
\end{array}
\right]
\end{eqnarray}
With these definitions, the model in \eq{simplemodel} can be expressed as a simple linear product, $y(t|\omega,\theta) = X_\omega\theta$, and the model and reference $\chi^2$ can be written
